Comparisons in three center

### 2020-12-13 scripts/43_comparisons_3.Rmd
jesus christ making tremendous advancements here

```{r}
sub_phenos %>% 
  imap(function(.x, .y){
    select(.data = .x, value) %>% 
      t() %>% 
      write.table(str_glue('../data/shotgun_output/humann2/{.y}.txt'), sep = '\t', quote = F, row.names = T, col.names = F)
  })
```

>>>>

```{r}
# the pheno for the different center and tox/CR_d30
sub_phenos %>% 
  imap(function(.x, .y){
    select(.data = .x, value) %>% 
      t() %>% 
      write.table(str_glue('../data/shotgun_output/humann2/{.y}.txt'), sep = '\t', quote = F, row.names = T, col.names = F)
  })
```

```{r}
# the pathway counts table
full <- read_tsv('../data/shotgun_output/humann2/humann2_pathabundance_CART.tsv') %>% 
  select(!ends_with('_1'), MS_UPENN_1)

pcts <- sub_phenos %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ full %>% select(`# Pathway`, matches(.x))) 
```
